A Unified Treatment of Tractability of Approximation Problems Defined on Hilbert Spaces

### 2023-07-18 GeneralizedTractability2023July17.tex
Fred M2 2023 Mac Updates

\documentclass[sort&compress]{elsarticle}
\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,booktabs,xspace}
\usepackage{epsfig}
\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
\usepackage{fdsymbol}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{cleveref}

@@

%TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''  \fred{Fred will do this.}

@@

\kachi{We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.}
In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability. We consider strong tractability when the information complexity is independent of the dimension, $d$. We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$. In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases. We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability. In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.

@@

\begin{definition}
    A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the \peter{information} complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}
We allow $\vp$ to be a scalar or vector as the situation dictates.
\end{definition}

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. (This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}\label{eq:Tlim}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.  Here, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases. A general reference
for results on algebraic tractability is \cite{NovWoz08a}, for exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.

\begin{table}
    \caption{Common forms of the tractability function, $T$.}
{\small
\begin{equation*}
	\begin{array}{r@{\quad}c@{\quad}cc}
		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{\peter{algebraic strong polynomial}} & \max\{1,\varepsilon^{-p}\} & 1\\
		\text{\peter{algebraic polynomial}} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
		\text{\peter{exponential strong polynomial}} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
		\text{\peter{exponential polynomial}} &
		[\max\{1,\log(1 + \varepsilon^{-1})\}]^p  d^{q} & d^{q} \\
        \text{\peter{algebraic quasi-polynomial}} &
        \exp\{p(1+\log(\max\{1,\log(1 + \varepsilon^{-1})\})(1+\log(d))\} &
        \exp\{p(1+\log(d))\}\\
        \text{\peter{exponential quasi-polynomial}} &
        \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}
	\end{array}
\end{equation*}}
\label{tab:commonT}
\end{table}

@@

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
\kachi{[KACHI: It seems the notation of the dimension has change from $d$ to $\delta$. I will work on this.]}
Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$. In particular, for  any $N\in\naturals$ with $n\ge N$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\thed,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\thed,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a}
    n - N +1 \ge T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, n, N \in \naturals.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.

@@

The argument proving equivalent conditions for tractability is similar to, but somewhat more involved than the proof of Theorem \ref{thm_main_strong_tract2}.  Moreover, the specification of the set of optimal parameters is not as precise as in Theorem \ref{thm_main_strong_tract2} \peter{[Is the latter sentence still true?]}.

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
Define
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\abs{B_d} < e\,M\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor e\,M\,d^{\tau_1} \rfloor$. Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \Leftrightarrow \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
\begin{eqnarray*}
d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=&d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&& + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le& d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le& e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
&\le & e\, M + \zeta (\tau_2 p).
\end{eqnarray*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

@@

Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strong $T$-separable tractability:
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
\end{equation*}
for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ satisfying the latter condition.
Theorem \ref{thm_main_tract2} yields the following equivalent condition for separable tractability:
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)}\psi(d,q)\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
\] for some $p,q >0$ and a positive constant $L_{(p,q)}$.
\end{example}
\kachi{Next, we will introduce another summarized \peter{[what do we mean by ``summarized''?]} notion of tractability. In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$. As will be seen below, this tractability function is equivalent \peter{[[I am not sure it is equivalent.]]} to the so-called \emph{quasi-polynomial tractability}.}
\
\begin{example}[Non-separable tractability]
    Suppose we define the tractability function $T$ by
\[
 T(\varepsilon^{-1},d,p)= \exp (p \, \hat{\phi}(\varepsilon^{-1})\, \hat{\psi}(d)) = [\exp( \hat{\phi}(\varepsilon^{-1}))]^{p \, \hat{\psi}(d)}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty),
\]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$.
We say that a problem is non-separable tractable with \peter{scalar} parameter $p$ iff there exists a positive $C_{p}$ such that

@@

Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability:
\[
\sup_{d\in\mathbb{N}}\sum_{\peter{i=\lceil L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}\rceil}} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, \peter{L_p >0}.
\]

@@

Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,p)= \exp[ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
\]
This can be rewritten as
\[
T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p.
\]
%Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$ \peter{[This sentence sounds a bit confusing to me---what exactly is meant by it?]}.
Then Theorem \ref{thm_main_tract2} yields the following equivalent condition for quasi-polynomial tractability in the algebraic case:
\[
\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, \peter{L_p >0}.\]
\end{example}
\peter{This essentially recovers \cite[Theorem 23.1]{NovWoz12a}.
}
Next, we will consider the exponential case as follows.
\begin{example}[Exponential quasi-polynomial tractability]

\noindent Suppose that the tractability function, $T$, is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p.
\]
%Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the exponential case:
\[
\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}\rceil}} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, \peter{L_p >0}.
\]
\peter{This essentially recovers \cite[Theorem 2]{KriWoz19a}.
}
\end{example}

@@

\section{Sub-$h$ Tractability}\label{sec:subh}
In this section we generalize the concept of weak tractability \peter{(see again \cite{NovWoz08a}--\cite{NovWoz12a})}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
\begin{equation} \label{eq:h_cond}
	h \text{ is strictly increasing}, \qquad
	h(0)=1, \qquad
 h(x+y) \ge  h(x)\cdot h(y)  \quad \forall x,y \ge 0.
\end{equation}
This means that $\log(h)$ is a superadditive function.  An example of the function $h$ is the exponential function, from which we can recover weak tractability.

Furthermore, let us denote the inverse function of $h$ by $h^{-1}$.
Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain \peter{from \eqref{eq:h_cond}}
\[
z w \le h (h^{-1}(z)+h^{-1}(w)),
\]
which yields by the monotonicity of $h^{-1}$ that
\begin{equation}\label{eq:submult_h_inverse}
h^{-1}(z w) \le h^{-1}(z)+h^{-1}(w).
\end{equation}
Now we define a generalized notion of weak tractability.
\begin{definition} \label{def:subhT}
	A problem is sub-$h$-$T$ tractable for parameter $\vp > \vzero$ if
	\begin{equation*}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\max(1,\comp(\varepsilon,d)))}{T(\varepsilon^{-1},d,\vp)} = 0.
	\end{equation*}
\end{definition}

>>>>

\documentclass[sort&compress]{elsarticle}
\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,booktabs,xspace}
\usepackage{epsfig}
\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
%\usepackage{fdsymbol} %removing this package solves the problem with \mathcal{I} not showing up properly.
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{cleveref}

@@

@@

We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.
In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability. We consider strong tractability when the information complexity is independent of the dimension, $d$. We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$. In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases. We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability. In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.

@@

\begin{definition}
    A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the information complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}
We allow $\vp$ to be a scalar or vector as the situation dictates.
\end{definition}

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. (This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}\label{eq:Tlim}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.  Here, $\vp = (p,q)$ in some cases, and $\vp$ is a scalar in other cases. A general reference
for results on algebraic tractability is \cite{NovWoz08a}.  For exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.

\begin{table}
    \caption{Common forms of the tractability function, $T$.}
{\small
\begin{equation*}
	\begin{array}{r@{\quad}c@{\quad}cc}
		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{algebraic strong polynomial} & \max\{1,\varepsilon^{-p}\} & 1\\
		\text{algebraic polynomial} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
		\text{exponential strong polynomial} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
		\text{exponential polynomial} &
		[\max\{1,\log(1 + \varepsilon^{-1})\}]^p  d^{q} & d^{q} \\
        \text{algebraic quasi-polynomial} &
        \exp\{p(1+\log(\max\{1,\log(1 + \varepsilon^{-1})\})(1+\log(d))\} &
        \exp\{p(1+\log(d))\}\\
        \text{exponential quasi-polynomial} &
        \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}
	\end{array}
\end{equation*}}
\label{tab:commonT}
\end{table}

@@

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$, and let $\thed \in \naturals$ be arbitrary. %\delta replaced d'
Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$. In particular, for  any $N\in\naturals$ with $n\ge N$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\thed,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\thed,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a}
    n - N +1 \ge T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, n, N \in \naturals.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.

@@

The argument proving equivalent conditions for tractability is similar to, but somewhat more involved than the proof of Theorem \ref{thm_main_strong_tract2}.  The lower limit on the sum is somewhat more complicated as well.

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
Define
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\abs{B_d} < e\,M\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor e\,M\,d^{\tau_1} \rfloor$. Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
\begin{align*}
d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
&\le  e\, M + \zeta (\tau_2 p).
\end{align*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

@@

Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strong $T$-separable tractability:
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
\end{equation*}
for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ satisfying the latter condition.
Theorem \ref{thm_main_tract2} yields the following equivalent condition for separable tractability:
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)}\psi(d,q)\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
\] for some $p,q >0$ and a positive constant $L_{(p,q)}$.
\end{example}
\kachi{Next, we will introduce another summarized \peter{[what do we mean by ``summarized''?]} notion of tractability. In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$. As will be seen below, this tractability function is equivalent \peter{[[I am not sure it is equivalent.]]} to the so-called \emph{quasi-polynomial tractability}.}
\
\begin{example}[Non-separable tractability]
    Suppose we define the tractability function $T$ by
\[
 T(\varepsilon^{-1},d,p)= \exp (p \, \hat{\phi}(\varepsilon^{-1})\, \hat{\psi}(d)) = [\exp( \hat{\phi}(\varepsilon^{-1}))]^{p \, \hat{\psi}(d)}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty),
\]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$.
We say that a problem is non-separable tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that

@@

Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability:
\[
\sup_{d\in\mathbb{N}}\sum_{i=\lceil L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}\rceil} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, L_p >0.
\]

@@

Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,p)= \exp[ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
\]
This can be rewritten as
\[
T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p.
\]
%Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$ \peter{[This sentence sounds a bit confusing to me---what exactly is meant by it?]}.
Then Theorem \ref{thm_main_tract2} yields the following equivalent condition for quasi-polynomial tractability in the algebraic case:
\[
\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
\end{example}
This essentially recovers \cite[Theorem 23.1]{NovWoz12a}.

Next, we will consider the exponential case as follows.
\begin{example}[Exponential quasi-polynomial tractability]

\noindent Suppose that the tractability function, $T$, is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p.
\]
%Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the exponential case:
\[
\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, L_p >0.
\]
This essentially recovers \cite[Theorem 2]{KriWoz19a}.
\end{example}

@@

\section{Sub-$h$ Tractability}\label{sec:subh}
In this section we generalize the concept of weak tractability (see again \cite{NovWoz08a}--\cite{NovWoz12a}).  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
\begin{equation} \label{eq:h_cond}
	h \text{ is strictly increasing}, \qquad
	h(0)=1, \qquad
 h(x+y) \ge  h(x)\cdot h(y)  \quad \forall x,y \ge 0.
\end{equation}
This means that $\log(h)$ is a superadditive function.  An example of the function $h$ is the exponential function, from which we can recover weak tractability.

Furthermore, let us denote the inverse function of $h$ by $h^{-1}$.
Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain from \eqref{eq:h_cond}
\[
z w \le h (h^{-1}(z)+h^{-1}(w)),
\]
which yields by the monotonicity of $h^{-1}$ that
\begin{equation}\label{eq:submult_h_inverse}
h^{-1}(z w) \le h^{-1}(z)+h^{-1}(w).
\end{equation}
Now we define a generalized notion of weak tractability.
\begin{definition} \label{def:subhT}
	A problem is sub-$h$-$T$ tractable for parameter $\vp > \vzero$ if
	\begin{equation*}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\max(1,\comp(\varepsilon,d)))}{T(\varepsilon^{-1},d,\vp)} = 0.
	\end{equation*}
\end{definition}
